Classless Java

### 2016-03-24 OOPSLA16/sections/Overview.tex
Conclusions first pass

\section{A Running Example: Animals}\label{sec:ep}

\begin{figure*}
\centering
\saveSpaceFig
\begin{tabular}{c|c}
\includegraphics[height=4cm]{pdfs/PegasusDetail.pdf}\hspace{20pt} &
\begin{minipage}{7cm}
\vspace{-90pt}
\lstinputlisting[linerange=6-17]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_JAVA
%basicstyle=\ttfamily\scriptsize
\end{minipage}
\end{tabular}
\caption{The animal system (left: complete structure, right: code for simplified animal system).}\label{fig:pegasus}
\end{figure*}

@@

\subsection{Object Interfaces and Subtyping}
\Q@Bird@s are \Q@Animal@s, but while \Q@Animal@s only need 2D
locations, \Q@Bird@s need 3D locations. Therefore when the \texttt{Bird}
interface extends the \Q@Animal@ interface, the notion of points needs to
be \emph{refined}. Such kind of refinement is challenging
in typical class-based approaches. Fortunately, with object interfaces,
we are able to provide a simple and effective solution.

\paragraph{Unsatisfactory class-based solutions to field type refinement}
In Java if we want to define an animal class with a field we have a set of
unsatisfactory options in front of us:
\begin{itemize}
\item Define a \Q@Point3D@ field in \Q@Animal@: this is bad since all animals
  would require more than needed.
  %Also it requires the programmer to predict the future, or
  Also it requires adapting the old code to accommodate for new evolutions.

@@

\begin{figure*}
\centering
\saveSpaceFig
\begin{tabular}{|l|l|l|l|}
\hline
& \textbf{Operation}  & \textbf{Example}                  & \textbf{Description } \\ \hline
\multirow{4}{*}{\parbox{2.5cm}{State operations (for a field \texttt{x})}} & \textbf{``fields''/getters}        &   \Q@int x()@                  & Retrieves value from field \texttt{x}.          \\ \cline{2-4}
& {\bf withers}        &   \Q@Point2D withX(int val)@                & Clones
object; updates field \texttt{x} to \texttt{val}.             \\ \cline{2-4}
& \textbf{setters}        & \Q@void x(int val)@ & Sets the field
\texttt{x} to a  new value \texttt{val}.        \\ \cline{2-4}
& \textbf{fluent setters}        & \Q@Point2D x(int val)@ &Sets the field
\texttt{x} to \texttt{val} and returns \texttt{\this}.           \\ \hline
\multirow{3}{*}{Other operations} &
\textbf{factory methods} &
%\begin{tabular}{l}
\Q@static Point2D of(int _x,int _y)@
%\end{tabular}
 & Factory method (generated).        \\
\cline{2-4}
& \textbf{functional updaters}        & \Q@Point3D with(Point2D val)@
& Update all matching fields in \texttt{val}.        \\ \hline
%\cline{2-4}
%& \textbf{imperative updaters}        & \Q@Point3D set(Point2D val)@ &
%Set all matching fields in \texttt{val}.        \\ \hline
\end{tabular}

>>>>

\section{A Running Example: Animals}\label{sec:ep}
\begin{figure*}
\centering
\saveSpaceFig
\begin{tabular}{c|c}
\includegraphics[height=4cm]{pdfs/PegasusDetail.pdf}\hspace{20pt} &
\begin{minipage}{7cm}
\vspace{-90pt}
\lstinputlisting[linerange=6-17]{../UseMixinLombok/src/pegasus/simple/java8/Main.java}% APPLY:linerange=PEGASUS_JAVA
%basicstyle=\ttfamily\scriptsize
\end{minipage}
\end{tabular}
\caption{The animal system (left: complete structure, right: code for simplified animal system).}\label{fig:pegasus}
\end{figure*}

@@

\subsection{Object Interfaces and Subtyping}
\Q@Bird@s are \Q@Animal@s, but while \Q@Animal@s only need 2D
locations, \Q@Bird@s need 3D locations. Therefore when the \texttt{Bird}
interface extends the \Q@Animal@ interface, the notion of points needs to
be \emph{refined}. Such kind of refinement is challenging
in typical \classbased approaches. Fortunately, with object interfaces,
we are able to provide a simple and effective solution.

\paragraph{Unsatisfactory \classbased solutions to field type refinement}
In Java if we want to define an animal class with a field we have a set of
unsatisfactory options in front of us:
\begin{itemize}
\item Define a \Q@Point3D@ field in \Q@Animal@: this is bad since all animals
  would require more than needed.
  %Also it requires the programmer to predict the future, or
  Also it requires adapting the old code to accommodate for new evolutions.

@@

\begin{figure*}
\saveSpaceFig
\centering
\begin{tabular}{|l|l|l|l|}
\hline
& \textbf{Operation}  & \textbf{Example}                  & \textbf{Description } \\ \hline
\multirow{4}{*}{\parbox{2.5cm}{State operations (for a field \texttt{x})}} & \textbf{``fields''/getters}        &   \Q@int x()@                  & Retrieves value from field \texttt{x}.          \\ \cline{2-4}
& {\bf withers}        &   \Q@Point2D withX(int val)@                & Clones
object; updates field \texttt{x} to \texttt{val}.             \\ \cline{2-4}
& \textbf{setters}        & \Q@void x(int val)@ & Sets the field
\texttt{x} to a  new value \texttt{val}.        \\ \cline{2-4}
& \textbf{fluent setters}        & \Q@Point2D x(int val)@ &Sets the field
\texttt{x} to \texttt{val} and returns \texttt{\this}.           \\ \hline
\multirow{3}{*}{Other operations} &
\textbf{factory methods} &
%\begin{tabular}{l}
\Q@static Point2D of(int _x,int _y)@
%\end{tabular}
 & Factory method (generated).        \\
\cline{2-4}
& \textbf{functional updaters}        & \Q@Point3D with(Point2D val)@
& Update all matching fields in \texttt{val}.        \\ \hline
%\cline{2-4}
%& \textbf{imperative updaters}        & \Q@Point3D set(Point2D val)@ &
%Set all matching fields in \texttt{val}.        \\ \hline
\end{tabular}
